Programming Assignment 2

### 2015-04-02 paper.tex
Discussed noise and comments of lvq

>>>>

\subsection{Performance}
Our LVQ had some pretty good performance but also some poor performance.  When testing animals against eachother (dogs, elephants, and giraffes) the network maintained a fairly consistent classification.  40

\subsection{Sensitivity}
Being a feed-back network, the LVQ did fairly well to adapt to small amounts of noise. Because the centroids themselves had noise, the LVQ did the best overall out of all implementations. Being able to try over and over to get the actual centroid from a distorted image really helped aleviate a lot of the problems that came with the noise.

\subsection{Comments}
Because we used the neural net toolkit, constructing the lvq required the most work. This seems paradoxical, but the lack of easy-to-locate documentation on the neural net toolkit and the functions it provides set us back quite a ways.
